%-------------------------------------------------------------------------------
% Methodology
%-------------------------------------------------------------------------------

\chapter{Core Research Objectives}\label{chap:objectives}

The primary objective of this thesis is to utilize the LLaMEA framework to autonomously design problem-specific optimization algorithms across the 24 standard BBOB functions, specifically when their landscapes are corrupted by artificial noise.

\section{RQ1: The Noise Injection Methodology}
\textbf{Question:} How can controlled statistical noise be systematically injected into standard BBOB functions to simulate real-world uncertainty? \\
\textbf{Approach:} The framework will utilize the \texttt{ioh} library to instantiate the base BBOB functions. We will construct a stochastic wrapper to apply Additive Gaussian Noise ($f_{noisy}(x) = f_{clean}(x) + \epsilon$, where $\epsilon \sim \mathcal{N}(0, \sigma^2)$). This models a highly realistic sensor environment by simulating the constant background electrical interference and thermal noise that persists independently of the signal's magnitude. This establishes a persistent noise floor that the algorithm must learn to cut through.

\section{RQ2: Per-Problem LLM Algorithm Creation}
\textbf{Question:} Can Large Language Models autonomously design specialized, problem-specific optimization algorithms that are resilient to noise? \\
\textbf{Approach:} The LLM will iteratively generate Python code via the LLaMEA framework. By overriding the execution sandbox, the library will natively coach the LLM into designing bespoke noise-handling mechanisms (e.g., surrogate modeling, momentum, or dynamic sampling) specifically tailored to exploit the topology of the current target problem.

\section{RQ3: The Comparative Benchmarking Framework}
\textbf{Question:} How do these noise-specialized, LLM-generated algorithms compare to existing LLM-generated algorithms (trained strictly on clean landscapes) and traditional heuristics when subjected to real-world noise? \\
\textbf{Approach:} A recent study successfully utilized LLaMEA to generate specialized algorithms for clean BBOB functions. This thesis establishes a rigorous A/B benchmark based purely on Global Minima Performance:
\begin{itemize}
    \item \textbf{Control Baselines:} We will execute traditional algorithms (Vanilla CMA-ES and Nelder-Mead) alongside the ``clean-trained'' LLM algorithms from existing literature on our noisy BBOB environments.
    \item \textbf{Novel Performance:} We will evaluate our 24 locally evolved ``noise-trained'' LLM algorithms.
    \item \textbf{Analysis:} We will conduct a white-box inspection of the generated Python code to document why the LLM succeeded, isolating the novel noise-handling mathematics it was forced to invent to beat the clean-trained baselines.
\end{itemize}